### 2018-05-07 chapters/04-killings.tex
beta 2! :)

\begin{table}[H]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{Base variables} &  &  &  &  &  \\
Log GDP per capita & -0.0091 & 0.0052 & 76.055 & 0.9335 & 226707 \\
 &  &  &  &  &  \\
\textit{Additional variables} &  &  &  &  &  \\
Post-Cold War years & -0.0133 & 0.0085 & 72.845 & 0.9472 & 35614 \\
UCDP civil war onset & 0.0529 & 0.0321 & 52.378 & 0.9441 & 20854 \\
Previous riots & 0.0140 & 0.0100 & 56.242 & 0.9216 & 35614 \\
UCDP ongoing civil war & 0.0172 & 0.0115 & 65.652 & 0.9092 & 20854 \\
Ethnic diversity (ELF) & 0.0184 & 0.0137 & 56.674 & 0.9050 & 35614 \\
Polity IV squared & -0.0002 & 0.0001 & 61.206 & 0.9031 & 35614 \\ \hline
\end{tabular}
\caption{Extreme Bounds Analysis -- Mass Killings (robust variables only)}
\label{tab:eba1}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{UCDP data} &  &  &  &  &  \\
Territory aims & -0.044 & 0.019 & 74.997 & 0.9804 & 17902 \\
Post-Cold War years & -0.038 & 0.019 & 66.574 & 0.9222 & 17902 \\
 &  &  &  &  &  \\
\textit{COW data} &  &  &  &  &  \\
Physical integrity & 0.024 & 0.013 & 66.674 & 0.9564 & 17902 \\
Militias & -0.099 & 0.048 & 73.104 & 0.9490 & 17902 \\
Years since last mass killing & 0.006 & 0.002 & 88.208 & 0.9472 & 101583 \\
Previous riots & 0.078 & 0.041 & 65.412 & 0.9348 & 17902 \\
Ethnic diversity (ELF) & 0.095 & 0.062 & 48.615 & 0.9000 & 17902 \\
 &  &  &  &  &  \\
\textit{Cederman et al. data} &  &  &  &  &  \\
Territory aims & -0.051 & 0.026 & 74.288 & 0.9167 & 17902 \\
Militias & -0.050 & 0.035 & 52.240 & 0.9101 & 17902 \\ \hline
\end{tabular}
\caption{EBA -- Mass killings during civil wars (robust variables only)}
\label{tab:ucdp}
\end{table}

@@

\begin{figure}[h]
\includegraphics[width=.9\textwidth, height=8cm]{images/drf.pdf}
\caption{Distributed Random Forest -- Variable Importance (scaled)}
\label{fig:drfuv}
\end{figure}

@@

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk.pdf}
    \caption{Extreme Bounds Analysis -- Mass killings}
    \label{fig:mk}
\end{sidewaysfigure}
\clearpage

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{UCDP data} &  &  &  &  &  \\
Territory aims & -0.044 & 0.019 & 74.997 & 0.9804 & 17902 \\
Post-Cold War years & -0.038 & 0.019 & 66.574 & 0.9222 & 17902 \\
 &  &  &  &  &  \\
\textit{COW data} &  &  &  &  &  \\
Physical integrity & 0.024 & 0.013 & 66.674 & 0.9564 & 17902 \\
Militias & -0.099 & 0.048 & 73.104 & 0.9490 & 17902 \\
Years since last mass killing & 0.006 & 0.002 & 88.208 & 0.9472 & 101583 \\
Previous riots & 0.078 & 0.041 & 65.412 & 0.9348 & 17902 \\
Ethnic diversity (ELF) & 0.095 & 0.062 & 48.615 & 0.9000 & 17902 \\
 &  &  &  &  &  \\
\textit{Cederman et al. data} &  &  &  &  &  \\
Territory aims & -0.051 & 0.026 & 74.288 & 0.9167 & 17902 \\
Militias & -0.050 & 0.035 & 52.240 & 0.9101 & 17902 \\ \hline
\end{tabular}
\caption{EBA -- Mass killings during civil wars}
\label{tab:ucdp1}
\end{table}

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-ucdp.pdf}
    \caption{EBA -- Mass killings during civil wars (UCDP data)}
    \label{fig:mk-ucdp}
\end{sidewaysfigure}
\clearpage

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-ucdp.pdf}
    \caption{EBA -- Mass killings during civil wars (COW data)}
    \label{fig:mk-cow}
\end{sidewaysfigure}
\clearpage

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-ucdp.pdf}
    \caption{EBA -- Mass killings during ethnic civil wars (Cederman et al. data)}
    \label{fig:mk-eth}
\end{sidewaysfigure}
\clearpage

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{Base variables} &  &  &  &  &  \\
Log GDP per capita & 0.0082 & 0.0043 & 81.439 & 0.9504 & 40677 \\
 &  &  &  &  &  \\
\textit{Additional variables} &  &  &  &  &  \\
Post-Cold War years & -0.0121 & 0.0069 & 77.804 & 0.9609 & 5064 \\
UCDP civil war onset & 0.0523 & 0.0292 & 62.561 & 0.9574 & 3304 \\
Previous riots &0.0134 & 0.0084 & 65.936 & 0.9401 & 5064 \\
UCDP ongoing civil war & 0.0177 & 0.0094 & 72.367 & 0.9372 & 3304 \\
Polity IV squared & -0.0002 & 0.0001 & 66.035 & 0.9268 & 5064 \\ 
Ethnic diversity (ELF) & 0.0162 & 0.0110 & 70.794 & 0.9266 & 5064 \\\hline
\end{tabular}
\caption{EBA -- 3 variables in each regression model}
\label{tab:mk-3vars}
\end{table}

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-3vars.pdf}
    \caption{EBA -- 3 variables in each regression model}
    \label{fig:mk-3vars}
\end{sidewaysfigure}
\clearpage

@@

\begin{table}[!htpb]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{Base variables} &  &  &  &  &  \\
Log GDP per capita & -0.010 & 0.006 & 70.806 & 0.9161 & 50000 \\
 &  &  &  &  &  \\
\textit{Additional variables} &  &  &  &  &  \\
Post-Cold War years & -0.014 & 0.010 & 68.496 & 0.9336 & 9532 \\
UCDP civil war onset & 0.053 & 0.035 & 44.784 & 0.9308 & 5100 \\
Previous riots & 0.015 & 0.012 & 47.988 & 0.9047 & 9569 \\\hline
\end{tabular}
\caption{EBA -- 5 variables in each regression model}
\label{tab:mk-5vars}
\end{table}

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-5vars.pdf}
    \caption{EBA -- 5 variables in each regression model}
    \label{fig:mk-5vars}
\end{sidewaysfigure}
\clearpage

@@

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-high-vif.pdf}
    \caption{EBA -- VIF 2.5}
    \label{fig:mk-low-vif}
\end{sidewaysfigure}
\clearpage

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{Base variables} &  &  &  &  &  \\
Log GDP per capita & 0.434 & 0.223 & 75.570 & 0.9267 & 50000 \\
 &  &  &  &  &  \\
\textit{Additional variables} &  &  &  &  &  \\
UCDP civil war onset & 1.308 & 0.530 & 87.261 & 0.9742 & 4506 \\
Post-Cold War years & -0.911 & 0.428 & 70.456 & 0.9448 & 7890 \\
Previous riots & 0.744 & 0.38 & 66.778 & 0.9383 & 7805 \\
Polity IV squared & -0.015 & 0.008 & 68.038 & 0.9285 & 7975 \\ \hline
\end{tabular}
\caption{EBA -- Logistic model}
\label{tab:mk-logit}
\end{table}

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-logit.pdf}
    \caption{EBA -- Logistic model}
    \label{fig:mk-logit}
\end{sidewaysfigure}
\clearpage

\begin{table}[H]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{Base variables} &  &  &  &  &  \\
Log GDP per capita & -0.1924 & 0.1031 & 76.118 & 0.9258 & 50000 \\
 &  &  &  &  &  \\
\textit{Additional variables} &  &  &  &  &  \\
UCDP civil war onset & 0.6422 & 0.2582 & 89.225 & 0.9772 & 4501 \\
Previous riots & 0.3367 & 0.1743 & 71.813 & 0.9436 & 7851 \\
Post-Cold War years & -0.3709 & 0.1830 & 71.465 & 0.9404 & 7836 \\
Polity IV squared & -0.0061 & 0.0032 & 70.155 & 0.9315 & 7931 \\ \hline
\end{tabular}
\caption{EBA -- Probit model}
\label{tab:eba1}
\end{table}

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-probit.pdf}
    \caption{EBA -- Probit model}
    \label{fig:mk-probit}
\end{sidewaysfigure}
\clearpage

@@

\begin{figure}[H]
    \centering
    \includegraphics{images/drf-mk2.pdf}
    \caption{Variable importance -- Seed 44849999}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth, height=9cm]{images/drfdpp2.pdf}
    \caption{Partial plots -- Seed 44849999}
    \label{fig:my_label}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics{images/drf-mk3.pdf}
    \caption{Variable importance -- Seed 1502436}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth, height=9cm]{images/drfdpp3a.pdf}
    \caption{Partial plots -- Seed 1502436}
    \label{fig:my_label}
\end{figure}

@@

\subsection{Genocide/Politicide}
\label{sec:mk-other-variable}

@@

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/uamk.pdf}
    \caption{EBA -- Genocides and politicides}
    \label{fig:uamk}
\end{sidewaysfigure}
\clearpage

\subsubsection{Genocide/Politicide during Civil Wars}

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{UCDP data} &  &  &  &  &  \\
Excluded population & -0.037 & 0.022 & 64.524 & 0.9176 & 8758 \\
 &  &  &  &  &  \\
\textit{COW data} &  &  &  &  &  \\
Excluded population & -0.057 & 0.031 & 65.703 & 0.9570 & 8820 \\
Discriminated population & -0.050 & 0.029 & 53.850 & 0.93.67 & 8767 \\
Post-Cold War years & -0.019 & 0.013 & 42.531 & 0.9203 & 8904 \\
 &  &  &  &  &  \\
\textit{Cederman et al. data} &  &  &  &  &  \\
Assassination dummy & -0.009 & 0.006 & 47.723 & 0.9232 & 8828 \\ \hline
\end{tabular}
\caption{EBA -- Genocides and politicides}
\label{tab:uamk1}
\end{table}

\newpage
\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/uamk-ucdp.pdf}
    \caption{EBA -- Genocides and politicides during civil wars (UCDP data)}
    \label{fig:uamk-ucdp}
\end{sidewaysfigure}
\clearpage

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/uamk-ucdp.pdf}
    \caption{EBA -- Genocides and politicides during civil wars (COW data)}
    \label{fig:uamk-cow}
\end{sidewaysfigure}
\clearpage

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/uamk-ucdp.pdf}
    \caption{EBA -- Genocides and politicides during ethnic civil wars (Cederman et al. data)}
    \label{fig:uamk-eth}
\end{sidewaysfigure}
\clearpage

\newpage
\subsection{Genocide/Politicide -- Random Forests}

@@

\begin{figure}[H]
    \centering
    \includegraphics{images/drf-gp.pdf}
    \caption{Variable importance -- Genocide/Politicide}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth, height=9cm]{images/drfdpp4a.pdf}
    \caption{Partial plots -- Genocide/Politicide}
    \label{fig:my_label}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics{images/drf-gp1.pdf}
    \caption{Variable importance -- Genocide/Politicide (UCDP data)}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth, height=9cm]{images/drfdpp5a.pdf}
    \caption{Partial plots -- Genocide/Politicide (UCDP data)}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics{images/drf-gp2.pdf}
    \caption{Variable importance -- Genocide/Politicide (COW data)}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth, height=9cm]{images/drfdpp6a.pdf}
    \caption{Partial plots -- Genocide/Politicide (COW data)}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics{images/drf-gp3.pdf}
    \caption{Variable importance -- Genocide/Politicide (Cederman et al. data)}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth, height=9cm]{images/drfdpp7a.pdf}
    \caption{Partial plots -- Genocide/Politicide (Cederman et al. data)}
    \label{fig:my_label}
\end{figure}

>>>>

\begin{table}[H]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{Base variables} &  &  &  &  &  \\
Log GDP per capita & -0.0091 & 0.0052 & 76.055 & 0.9335 & 226707 \\
 &  &  &  &  &  \\
\textit{Additional variables} &  &  &  &  &  \\
Post-Cold War years & -0.0133 & 0.0085 & 72.845 & 0.9472 & 35614 \\
UCDP civil war onset & 0.0529 & 0.0321 & 52.378 & 0.9441 & 20854 \\
Previous riots & 0.0140 & 0.0100 & 56.242 & 0.9216 & 35614 \\
UCDP ongoing civil war & 0.0172 & 0.0115 & 65.652 & 0.9092 & 20854 \\
Ethnic diversity (ELF) & 0.0184 & 0.0137 & 56.674 & 0.9050 & 35614 \\
Polity IV squared & -0.0002 & 0.0001 & 61.206 & 0.9031 & 35614 \\ \hline
\end{tabular}
\caption{Extreme Bounds Analysis -- Mass Killings (Robust Variables Only)}
\label{tab:eba1}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{UCDP data} &  &  &  &  &  \\
Territory aims & -0.044 & 0.019 & 74.997 & 0.9804 & 17902 \\
Post-Cold War years & -0.038 & 0.019 & 66.574 & 0.9222 & 17902 \\
 &  &  &  &  &  \\
\textit{COW data} &  &  &  &  &  \\
Physical integrity & 0.024 & 0.013 & 66.674 & 0.9564 & 17902 \\
Militias & -0.099 & 0.048 & 73.104 & 0.9490 & 17902 \\
Years since last mass killing & 0.006 & 0.002 & 88.208 & 0.9472 & 101583 \\
Previous riots & 0.078 & 0.041 & 65.412 & 0.9348 & 17902 \\
Ethnic diversity (ELF) & 0.095 & 0.062 & 48.615 & 0.9000 & 17902 \\
 &  &  &  &  &  \\
\textit{Cederman et al. data} &  &  &  &  &  \\
Territory aims & -0.051 & 0.026 & 74.288 & 0.9167 & 17902 \\
Militias & -0.050 & 0.035 & 52.240 & 0.9101 & 17902 \\ \hline
\end{tabular}
\caption{EBA -- Mass Killings during Civil Wars (Robust Variables Only)}
\label{tab:ucdp}
\end{table}

@@

\begin{figure}[h]
\includegraphics[width=.9\textwidth, height=8cm]{images/drf.pdf}
\caption{Distributed Random Forest -- Variable Importance (Scaled)}
\label{fig:drfuv}
\end{figure}

@@

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk.pdf}
    \caption{Extreme Bounds Analysis -- Mass Killings}
    \label{fig:mk}
\end{sidewaysfigure}
\clearpage

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{UCDP data} &  &  &  &  &  \\
Territory aims & -0.044 & 0.019 & 74.997 & 0.9804 & 17902 \\
Post-Cold War years & -0.038 & 0.019 & 66.574 & 0.9222 & 17902 \\
 &  &  &  &  &  \\
\textit{COW data} &  &  &  &  &  \\
Physical integrity & 0.024 & 0.013 & 66.674 & 0.9564 & 17902 \\
Militias & -0.099 & 0.048 & 73.104 & 0.9490 & 17902 \\
Years since last mass killing & 0.006 & 0.002 & 88.208 & 0.9472 & 101583 \\
Previous riots & 0.078 & 0.041 & 65.412 & 0.9348 & 17902 \\
Ethnic diversity (ELF) & 0.095 & 0.062 & 48.615 & 0.9000 & 17902 \\
 &  &  &  &  &  \\
\textit{Cederman et al. data} &  &  &  &  &  \\
Territory aims & -0.051 & 0.026 & 74.288 & 0.9167 & 17902 \\
Militias & -0.050 & 0.035 & 52.240 & 0.9101 & 17902 \\ \hline
\end{tabular}
\caption{EBA -- Mass Killings during Civil Wars}
\label{tab:ucdp1}
\end{table}

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-ucdp.pdf}
    \caption{EBA -- Mass Killings during Civil Wars (UCDP Data)}
    \label{fig:mk-ucdp}
\end{sidewaysfigure}
\clearpage

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-cow.pdf}
    \caption{EBA -- Mass Killings during Civil Wars (COW Data)}
    \label{fig:mk-cow}
\end{sidewaysfigure}
\clearpage

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-eth.pdf}
    \caption{EBA -- Mass Killings during ethnic civil wars (Cederman et al. Data)}
    \label{fig:mk-eth}
\end{sidewaysfigure}
\clearpage

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{Base variables} &  &  &  &  &  \\
Log GDP per capita & 0.0082 & 0.0043 & 81.439 & 0.9504 & 40677 \\
 &  &  &  &  &  \\
\textit{Additional variables} &  &  &  &  &  \\
Post-Cold War years & -0.0121 & 0.0069 & 77.804 & 0.9609 & 5064 \\
UCDP civil war onset & 0.0523 & 0.0292 & 62.561 & 0.9574 & 3304 \\
Previous riots &0.0134 & 0.0084 & 65.936 & 0.9401 & 5064 \\
UCDP ongoing civil war & 0.0177 & 0.0094 & 72.367 & 0.9372 & 3304 \\
Polity IV squared & -0.0002 & 0.0001 & 66.035 & 0.9268 & 5064 \\ 
Ethnic diversity (ELF) & 0.0162 & 0.0110 & 70.794 & 0.9266 & 5064 \\\hline
\end{tabular}
\caption{EBA -- 3 Variables}
\label{tab:mk-3vars}
\end{table}

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-3vars.pdf}
    \caption{EBA -- 3 Variables}
    \label{fig:mk-3vars}
\end{sidewaysfigure}
\clearpage

@@

\begin{table}[!htpb]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{Base variables} &  &  &  &  &  \\
Log GDP per capita & -0.010 & 0.006 & 70.806 & 0.9161 & 50000 \\
 &  &  &  &  &  \\
\textit{Additional variables} &  &  &  &  &  \\
Post-Cold War years & -0.014 & 0.010 & 68.496 & 0.9336 & 9532 \\
UCDP civil war onset & 0.053 & 0.035 & 44.784 & 0.9308 & 5100 \\
Previous riots & 0.015 & 0.012 & 47.988 & 0.9047 & 9569 \\\hline
\end{tabular}
\caption{EBA -- 5 Variables}
\label{tab:mk-5vars}
\end{table}

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-5vars.pdf}
    \caption{EBA -- 5 Variables}
    \label{fig:mk-5vars}
\end{sidewaysfigure}
\clearpage

@@

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-low-vif.pdf}
    \caption{EBA -- VIF 2.5}
    \label{fig:mk-low-vif}
\end{sidewaysfigure}
\clearpage

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{Base variables} &  &  &  &  &  \\
Log GDP per capita & 0.434 & 0.223 & 75.570 & 0.9267 & 50000 \\
 &  &  &  &  &  \\
\textit{Additional variables} &  &  &  &  &  \\
UCDP civil war onset & 1.308 & 0.530 & 87.261 & 0.9742 & 4506 \\
Post-Cold War years & -0.911 & 0.428 & 70.456 & 0.9448 & 7890 \\
Previous riots & 0.744 & 0.38 & 66.778 & 0.9383 & 7805 \\
Polity IV squared & -0.015 & 0.008 & 68.038 & 0.9285 & 7975 \\ \hline
\end{tabular}
\caption{EBA -- Logistic Regression}
\label{tab:mk-logit}
\end{table}

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-logit.pdf}
    \caption{EBA -- Logistic Regression}
    \label{fig:mk-logit}
\end{sidewaysfigure}
\clearpage

\begin{table}[H]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{Base variables} &  &  &  &  &  \\
Log GDP per capita & -0.1924 & 0.1031 & 76.118 & 0.9258 & 50000 \\
 &  &  &  &  &  \\
\textit{Additional variables} &  &  &  &  &  \\
UCDP civil war onset & 0.6422 & 0.2582 & 89.225 & 0.9772 & 4501 \\
Previous riots & 0.3367 & 0.1743 & 71.813 & 0.9436 & 7851 \\
Post-Cold War years & -0.3709 & 0.1830 & 71.465 & 0.9404 & 7836 \\
Polity IV squared & -0.0061 & 0.0032 & 70.155 & 0.9315 & 7931 \\ \hline
\end{tabular}
\caption{EBA -- Probit Regression}
\label{tab:eba1}
\end{table}

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/mk-probit.pdf}
    \caption{EBA -- Probit Regression}
    \label{fig:mk-probit}
\end{sidewaysfigure}
\clearpage

@@

\begin{figure}[H]
    \centering
    \includegraphics{images/drf-mk2.pdf}
    \caption{Variable Importance -- Seed 44849999}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth, height=9cm]{images/drfdpp2.pdf}
    \caption{Partial Plots -- Seed 44849999}
    \label{fig:my_label}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics{images/drf-mk3.pdf}
    \caption{Variable Importance -- Seed 1502436}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth, height=9cm]{images/drfdpp3a.pdf}
    \caption{Partial Plots -- Seed 1502436}
    \label{fig:my_label}
\end{figure}

@@

\subsection{Genocides/Politicides}
\label{sec:mk-other-variable}

@@

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/uamk.pdf}
    \caption{EBA -- Genocides/Politicides}
    \label{fig:uamk}
\end{sidewaysfigure}
\clearpage

\subsubsection{Genocides/Politicides during Civil Wars}

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrrrr}
\hline
\textbf{Variable} & \textbf{Avg. $\beta$} & \textbf{Avg. SE} & \textbf{$\%$ Sig.} & \textbf{CDF(0)} & \textbf{Models} \\ \hline
\textit{UCDP data} &  &  &  &  &  \\
Excluded population & -0.037 & 0.022 & 64.524 & 0.9176 & 8758 \\
 &  &  &  &  &  \\
\textit{COW data} &  &  &  &  &  \\
Excluded population & -0.057 & 0.031 & 65.703 & 0.9570 & 8820 \\
Discriminated population & -0.050 & 0.029 & 53.850 & 0.93.67 & 8767 \\
Post-Cold War years & -0.019 & 0.013 & 42.531 & 0.9203 & 8904 \\
 &  &  &  &  &  \\
\textit{Cederman et al. data} &  &  &  &  &  \\
Assassination dummy & -0.009 & 0.006 & 47.723 & 0.9232 & 8828 \\ \hline
\end{tabular}
\caption{EBA -- Genocides/Politicides}
\label{tab:uamk1}
\end{table}

\newpage
\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/uamk-ucdp.pdf}
    \caption{EBA -- Genocides and Politicides during Civil Wars (UCDP Data)}
    \label{fig:uamk-ucdp}
\end{sidewaysfigure}
\clearpage

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/uamk-cow.pdf}
    \caption{EBA -- Genocides and Politicides during Civil Wars (COW Data)}
    \label{fig:uamk-cow}
\end{sidewaysfigure}
\clearpage

\clearpage
\begin{sidewaysfigure}
    \centering
    \includegraphics[width=\textwidth]{images/uamk-eth.pdf}
    \caption{EBA -- Genocides and Politicides during Ethnic Civil Wars (Cederman et al. Data)}
    \label{fig:uamk-eth}
\end{sidewaysfigure}
\clearpage

\newpage
\subsection{Genocides/Politicides -- Random Forests}

@@

\begin{figure}[H]
    \centering
    \includegraphics{images/drf-gp.pdf}
    \caption{Variable Importance -- Genocides/Politicides}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth, height=9cm]{images/drfdpp4a.pdf}
    \caption{Partial Plots -- Genocides/Politicides}
    \label{fig:my_label}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics{images/drf-gp1.pdf}
    \caption{Variable Importance -- Genocides/Politicides (UCDP Data)}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth, height=9cm]{images/drfdpp5a.pdf}
    \caption{Partial Plots -- Genocides/Politicides (UCDP Data)}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics{images/drf-gp2.pdf}
    \caption{Variable Importance -- Genocides/Politicides (COW Data)}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth, height=9cm]{images/drfdpp6a.pdf}
    \caption{Partial Plots -- Genocides/Politicides (COW Data)}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics{images/drf-gp3.pdf}
    \caption{Variable Importance -- Genocides/Politicides (Cederman et al. Data)}
    \label{fig:my_label}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth, height=9cm]{images/drfdpp7a.pdf}
    \caption{Partial Plots -- Genocides/Politicides (Cederman et al. Data)}
    \label{fig:my_label}
\end{figure}
